Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-05 draft/accordionComplexSurfaces.tex
abstract

\begin{abstract}
We consider three combinatorial models for the support $\tau$-tilting complex of a locally gentle bound quiver: the accordion complex, the slalom complex, and the non-kissing complex. We unify these models in the same picture.
\end{abstract}

@@

\yann{Abstract to do.}

@@

%We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a quiver~$Q$ and an admissible ideal~$I$ of the path algebra~$kQ$, so that the quotient algebra~$kQ/I$ is finite dimensional.
We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a quiver~$Q$ and an ideal~$I$ of the path algebra~$kQ$ such that $I$ is generated by linear combinations of paths of length at least two.
Note that we \textbf{do not require} that the quotient algebra~$kQ/I$ be finite dimensional.

\begin{definition}[\cite{ButlerRingel}]
\label{def:gentleQuiver}
A \defn{locally gentle bound quiver}~$\bar Q \eqdef (Q,I)$ is a bound quiver such that
\begin{itemize}
\item each vertex~$v \in Q_0$ has at most two incoming and two outgoing arrows,
\item the ideal~$I$ is generated by paths of length exactly two,
\item for any arrow~$\beta \in Q_1$, there is at most one arrow~$\alpha \in Q_1$ such that~$t(\alpha) = s(\beta)$ and~${\alpha\beta\notin I}$ (resp.~$\alpha\beta \in I$) and at most one arrow~$\gamma \in Q_1$ such that~$t(\beta) = s(\gamma)$~and~${\beta\gamma\notin I}$~(resp.~${\beta\gamma \in I}$).
\end{itemize}
The algebra~$kQ/I$ is called a \defn{locally gentle algebra}.
A \defn{gentle bound quiver} is a locally bound quiver~$\bar Q$ such that the algebra $kQ/I$ is finite-dimensional; the algebra is then called a \defn{gentle algebra}.
\end{definition}

>>>>

\begin{abstract}
Starting from a locally gentle bound quiver, we define on the one hand a simplicial complex, called the non-kissing complex.
On the other hand, we construct a punctured, marked, oriented surface with boundary, endowed with a pair of dual dissections.
From those geometric data, we define two simplicial complexes: the accordion complex, and the slalom complex, generalising work of A. Garver and T. McConville in the case of a disk.
We show that all three simplicial complexes are isomorphic.
We also construct inverse bijections between the set of isomorphism classes of locally gentle bound quivers and the set of homeomorphism classes of punctured, marked, oriented surfaces with boundary, endowed with a pair of dual dissections.
\end{abstract}

@@

@@

%We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a quiver~$Q$ and an admissible ideal~$I$ of the path algebra~$kQ$, so that the quotient algebra~$kQ/I$ is finite dimensional.
We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a finite quiver~$Q$ and an ideal~$I$ of the path algebra~$kQ$ such that $I$ is generated by linear combinations of paths of length at least two.
Note that we \textbf{do not require} that the quotient algebra~$kQ/I$ be finite dimensional.

\begin{definition}[\cite{ButlerRingel}]
\label{def:gentleQuiver}
A \defn{locally gentle bound quiver}~$\bar Q \eqdef (Q,I)$ is a bound quiver such that
\begin{itemize}
\item each vertex~$v \in Q_0$ has at most two incoming and two outgoing arrows,
\item the ideal~$I$ is generated by paths of length exactly two,
\item for any arrow~$\beta \in Q_1$, there is at most one arrow~$\alpha \in Q_1$ such that~$t(\alpha) = s(\beta)$ and~${\alpha\beta\notin I}$ (resp.~$\alpha\beta \in I$) and at most one arrow~$\gamma \in Q_1$ such that~$t(\beta) = s(\gamma)$~and~${\beta\gamma\notin I}$~(resp.~${\beta\gamma \in I}$).
\end{itemize}
The algebra~$kQ/I$ is called a \defn{locally gentle algebra}.
A \defn{gentle bound quiver} is a locally gentle bound quiver~$\bar Q$ such that the algebra $kQ/I$ is finite-dimensional; the algebra is then called a \defn{gentle algebra}.
\end{definition}
